---
title: "GG testing stats"
author: "Odysseas Morgan"
date: "4/14/2022"
output: pdf_document
---
**GG test processing Script**
(c) Odysseas Morgan 2022

To run this Script, run each block in sequence using Rstudio. Don't actually knit it into a pdf. 
Each block performs a particular step in the analysis of the data, and is labled accordingly. There is some residual terminal outputs from unit testing. This can largely be ignored.

Initialization
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Read in Dataset
```{r}
############# Select Dataset  ##############

csv <- read.csv(file.choose()) #open txt format
GGdataOG = data.frame(csv)
GGdata = GGdataOG
```

Create a Dataframe of Unique Assemblies
```{r}
# generate DF of unique assemblies
Sabotaged = c(0)
JunctType = c(0)
part1 = c(0)
part2 = c(0)
part3 = c(0)
part4 = c(0)
part5 = c(0)
part6 = c(0)
part7 = c(0)
part8 = c(0)
Sucesses = c(0)
Fails = c(0)
GGdataUni = data.frame(gID, JunctType, part1, part2, part3, part4, part5, part6, part7, part8, Sucesses, Fails)

noEntries = TRUE
for(rI in 1:nrow(GGdata)){
  row = GGdata[rI,]
  #print(all(row[1,4:11] == row[1,4:11]))
  addRow = TRUE
  matchI = 0
  addSuc = FALSE
  for(urI in 1:nrow(GGdataUni)){
    uRow = GGdataUni[urI,]
    #print(row[4:11])
    #print(uRow[3:10])
    #print(all(row[4:11] == uRow[3:10]))
    
    if(all(row[4:11] == uRow[3:10])){
      if(row[1,2] == "Yes"){
        addSuc = TRUE
      }
        
      addRow = FALSE
      matchI = urI
    }
    
  }
  if(addRow){
    uSuc = 0
    uFail = 1
      if(row[1,2] == "Yes"){
        uSuc = 1
        uFail = 0
      }
        newURow =   c("placeholder",as.character(row[1,3:11]), uSuc, uFail)
        #print(newURow)
        if(noEntries){
          GGdataUni[nrow(GGdataUni),] = newURow
          noEntries = FALSE
        } else {
          GGdataUni[nrow(GGdataUni) + 1,] = newURow
        }
  } else {
  
    if(addSuc){
      GGdataUni[matchI,11] = as.integer(GGdataUni[matchI,11]) + 1
    } else {
      GGdataUni[matchI,12] = as.integer(GGdataUni[matchI,12]) + 1
    }
  }
}
#creates copy dataframe
GGdataUniCopy = GGdataUni

```


Create part list (non-unique)
```{r}
#initial part list (old)

partLs = c()
partSuc = c()
partFail = c()
partFAs = c()
fails = 0

for(rI in 1:nrow(GGdata)){
  #for every assembly
  #print(rI)
  row = GGdata[rI,]
  if(row[,2] != "Yes"){
    fails = fails + 1
  }
  for(partI in 4:11){
    #for every possible part in the assembly
    part = row[,partI]
    #print("part")
    #print(part)
    #print(partI)
    if(!(part %in% partLs) && part != ""){
      # if part hasnt been seen before
      if(row[,2] == "Yes"){
        #if assembly is sucessful
        set = c(row[,partI], 1, 0)
        partFAs = append(partFAs, c())
      } else {
        #if assembly was a fail
        set = c(row[,partI], 0, 1)
        partFAs = append(partFAs, c(row[,1], 0))
        
      }
      #creates new entry for new part
      partLs = append(partLs, set[1])
      partSuc = append(partSuc, strtoi(set[2]))
      partFail = append(partFail, strtoi(set[3]))
      
    } else if(part != ""){
      #if part has been seen before
      ind = match(part, partLs)
      if(row[,2] == "Yes"){
        #if assembly is sucessful
        partSuc[ind] = strtoi(partSuc[ind]) + 1
      } else {
        #if assembly was a fail
        partFail[ind] = strtoi(partFail[ind]) + 1
        #partFAs[ind] = append(partFAs[ind], row[1])
      }
    }
  }
    
}
# partLs
# partFail
# partFAs
```

Create Part list (Unique)
```{r}
#initial part list (new)

partLs = c()
partUSuc = c()
partSuc = c()
partFail = c()
partUFail = c()
partFAs = c()
fails = 0
sucs = 0


for(rI in 1:nrow(GGdataUni)){
  #for every assembly
  #print(rI)
  row = GGdataUni[rI,]
  fails = fails + strtoi(row[1,12])
  sucs = sucs + strtoi(row[1,11])

  for(partI in 3:10){
    #for every possible part in the assembly
    part = row[,partI]
    #print("part")
    #print(part)
    #print(partI)
    if(!(part %in% partLs) && part != ""){
      # if part hasnt been seen before
      set = c(row[1,partI], row[1,11], row[1,12])
        
        #partFAs = append(partFAs, c(row[,1], 0))
      #creates new entry for new part
      partLs = append(partLs, set[1])
      partSuc = append(partSuc, strtoi(set[2]))
      partFail = append(partFail, strtoi(set[3]))
      if(strtoi(set[2]) >= strtoi(set[3])){
        partUSuc = append(partUSuc, 1)
        partUFail = append(partUFail, 0)
      }else {
        partUSuc = append(partUSuc, 0)
        partUFail = append(partUFail, 1)
      }
      
    }else if(part != ""){
      #if part has been seen before
      ind = match(part, partLs)
      partSuc[ind] = strtoi(partSuc[ind]) + strtoi(row[1,11])
      partFail[ind] = strtoi(partFail[ind]) + strtoi(row[1,12])
      #if suc >= fails, counts as a unique success
      if(strtoi(row[1,11]) >= strtoi(row[1,12])){
        partUSuc[ind] = partUSuc[ind] + 1
      }else{
        partUFail[ind] = partUFail[ind] + 1
      }
      #partFAs[ind] = append(partFAs[ind], row[1])
    
    }
  }
    
}




```


Detect saboteurs (non-unique)
```{r}
#Gen 2 Saboteur finder

#need to reset table to avoid second pass bug
GGdata = GGdataOG

#absolute saboteurs
saboteurs = c()
for(index in 1:length(partSuc)){
  if(partSuc[index]/(partSuc[index]+partFail[index]) <= 0){
    saboteurs = append(saboteurs, partLs[index])
  }
}

#first round of saboteur accounting
partFailAC = strtoi(partFail)
assFailAC = c()
assFailAC_tollerant = c()
assFailRaw = c()
assFailSab = c()
assSuc = c()

for(rI in 1:nrow(GGdata)){
  #for every assembly
  #print(rI)
  sabAC = FALSE
  row = GGdata[rI,]
  if(row[,2] != "Yes"){
    fails = fails + 1
    assFailRaw = append(assFailRaw, row[1,1])
  }
  for(partI in 4:11){
    #for every possible part in the assembly
    part = row[,partI]
    for(sab in saboteurs){
      if(part == sab){
        sabAC = TRUE
      }
    }
  }
  if(sabAC){
    GGdata[rI,2] = "Sabotaged"
    assFailSab = append(assFailSab, row[1,1])
    for(partI in 4:11){
      #for every possible part in the assembly
      part = row[,partI]
      partInd = match(part, partLs)
      partFailAC[partInd] = strtoi(partFailAC[partInd]) - 1
      #print(part)
    } 
  }else if(row[,2] != "Yes"){
    assFailAC = append(assFailAC, row[1,1])
    if(row[1,2] == "No"){
      assFailAC_tollerant = append(assFailAC_tollerant, row[1,1])
    }
  } else {
     assSuc = append(assSuc, row[1,1])
  }

    
}
#saboteurs
#saboteurs = append(saboteurs, "m1469")



#Threshold saboteurs

#threshold for sucess
threshold = 0.20



for(index in 1:length(partSuc)){
  #print(index)
  if(partSuc[index]!= 0 && (((partSuc[index]/(partSuc[index] + partFailAC[index])) <= threshold) || (partSuc[index] + partFailAC[index]) == 0)){
    saboteurs = append(saboteurs, partLs[index])
  }
}

saboteurs

#needs to remove threshold sucess saboteur assemblies?
#assSuc = c()

#needs to remove threshold fail saboteur assemblies
assFailAC =c()

for(rI in 1:nrow(GGdata)){
  #for every assembly
  #print(rI)
  sabAC = FALSE
  row = GGdata[rI,]
  if(row[,2] != "Yes" && row[,2] !="Sabotaged"){
    #print(row[,1])
    for(partI in 4:11){
      #for every possible part in the assembly
      part = row[,partI]
      for(sab in saboteurs){
        if(part == sab){
          sabAC = TRUE
        }
      }
    }
    if(sabAC){
      #print("new Sab")
      #print(row[,1])
    }
  }
  if(sabAC){
    GGdata[rI,2] = "Sabotaged"
    assFailSab = append(assFailSab, row[1,1])
    for(partI in 4:11){
      #for every possible part in the assembly
      part = row[,partI]
      partInd = match(part, partLs)
      partFailAC[partInd] = strtoi(partFailAC[partInd]) - 1
      #print(part)
    } 
  }else if(row[,2] != "Yes" && row[,2] != "Sabotaged"){
    assFailAC = append(assFailAC, row[1,1])
    if(row[1,2] == "No"){
      #assFailAC_tollerant = append(assFailAC_tollerant, row[1,1])
    }
  } else {
     assSuc = append(assSuc, row[1,1])
  }
}
saboteurs
assFailAC
assSuc
partFail
partFailAC
```

Detect Saboteur (Unique)
```{r}
# Saboteur scouring gen 3

#need to reset table to avoid second pass bug

GGdataUni = GGdataUniCopy

#absolute saboteurs
saboteurs = c()
for(index in 1:length(partUSuc)){
  if(partUSuc[index]/(partUSuc[index]+partUFail[index]) <= 0){
    saboteurs = append(saboteurs, partLs[index])
  }
}

saboteurs
#first round of saboteur accounting

partFailAC = strtoi(partFail)
partUFailAC = strtoi(partUFail)


for(rI in 1:nrow(GGdataUni)){
  #for every assembly
  #print(rI)
  sabAC = FALSE
  row = GGdataUni[rI,]
  if(row[11] == 0){
    assUFailRaw = append(assUFailRaw, row[1,12])
  }else{
    #assUSuc = append(assUSuc, row[1,11]) # included later, corner case of threshold saboteurs
  }
  for(partI in 3:10){
    #for every possible part in the assembly
    part = row[,partI]
    for(sab in saboteurs){
      if(part == sab){
        sabAC = TRUE
        #print(part)
      }
    }
  }
  if(sabAC){
    GGdataUni[rI,1] = TRUE
    
    for(partI in 3:10){
      #for every possible part in the assembly
      part = row[,partI]
      partInd = match(part, partLs)
      #remove failures that should be accounted failures
      partUFailAC[partInd] = strtoi(partUFailAC[partInd]) - 1
      partFailAC[partInd] = strtoi(partFailAC[partInd]) - strtoi(row[1,12])
    } 
  }
    
}
partUFailAC
print("pre")
#saboteurs
#saboteurs = append(saboteurs, "m1469")



#Threshold saboteurs
#cannot use unique assemblies


#threshold for sucess
threshold = 0.20

partSuc
partFailAC

for(index in 1:length(partSuc)){
  #print(index)
  #partUSuc might be wrong
  if(partSuc[index]!= 0 && (((partSuc[index]/(partSuc[index] + partFailAC[index])) <= threshold) || (partSuc[index] + partFailAC[index]) == 0)){
    saboteurs = append(saboteurs, partLs[index])
  }
}

# saboteurs

#needs to remove threshold success saboteur assemblies?
#assSuc = c()

####

#needs to remove threshold fail saboteur assemblies


# partUFailAC

for(rI in 1:nrow(GGdataUni)){
  #for every assembly
  #print(rI)
  sabAC = FALSE
  row = GGdataUni[rI,]
  if(row[1,1] != TRUE){ #kill me i know its ugly
    #print(row[,1])
    for(partI in 3:10){
      #for every possible part in the assembly
      part = row[1,partI]
      for(sab in saboteurs){
        if(part == sab){
          sabAC = TRUE
          print("identified Saboteur:")
          print(part)
        }
      }
    }
    # if(sabAC){
    #   #print("new Sab")
    #   #print(row[,1])
    # }
  }
  #account in part lists
  if(sabAC){
    # print("hello")
    GGdataUni[rI,1] = TRUE
    for(partI in 3:10){
      if(row[1,12] != 0){
        #for every possible part in the assembly
        part = row[,partI]
        if(part != ""){
          partInd = match(part, partLs)
          #remove accounted for failures
          partUFailAC[partInd] = strtoi(partUFailAC[partInd]) - 1
          #print(partUFailAC[partInd])
          # if(partUFailAC[partInd] < 0){
          #   print(part)
          # }
          #print(part)
        }
      }
    } 
  }
}
#saboteurs


###correct block###
```



```{r}
assUFailAC = c()
assUFailRaw = c()
assUFailSab = c()
assUSuc = c()
assUSucSab = c()
for(rI in 1:nrow(GGdataUni)){
  row = GGdataUni[rI,]
  if(row[1,1] == TRUE){#yes its ugly 
    if(row[1,12] != 0){
      assUFailRaw = append(assUFailRaw, row[1,12])
      assUFailSab = append(assUFailRaw, row[1,12])
    }else{
      assUSucSab = append(assUSucSab, row[1,11])
    }
  }else{
    if(row[1,12]!= 0){
      assUFailRaw = append(assUFailRaw, row[1,12])
      assUFailAC = append(assUFailAC, row[1,12])
      #print(row[1,1])
    }else{
      assUSuc = append(assUSuc, row[1,11])
    }
  }
}



```





```{r}

partSuc = strtoi(partSuc)
partFail = strtoi(partFail)
partFailAC = strtoi(partFailAC)
partUSuc = strtoi(partUSuc)
partUFail = strtoi(partUFail)
partUFailAC = strtoi(partUFailAC)

partSuc
partUSuc
partLs
# pRawRate = strtoi(partSuc) / (strtoi(partFail) + strtoi(partSuc))
# 
# pAcRate = strtoi(partSuc) / (strtoi(partFailAC) + strtoi(partSuc))
# 
# pAcRate
# pRawRate
# 
# 


partDF = data.frame(partLs, partSuc, partFail,partFailAC, partUSuc, partUFail, partUFailAC) # partFailAC, pRawRate, pAcRate)
partDF
write.csv(partDF,"/Users/odysseasmorgan/Chemistry/Thesis/Part_Sorting_Code/GG_part_performance.csv", row.names = FALSE)


```


Assembly Failure by part Breakdown graph
```{r}
#only unique assemblies counted

#General colors defined

#CSuc = "#0D37DF" # Intense blue
CSuc = "#5b45f6ff"

#CSabFail = "#EA4025" #Intense red
CSabFail ="#f14d3aff"
#CSabFail = "#fe7369ff"

CAcFail = "#E5BF40"

CSabSuc = "#5ECBA9"


#colorSet of display
colorSetParts = c(CSabFail, CAcFail)


ggplot(partDF) + geom_bar(stat = "identity", aes(x = partLs, y = partUFail, fill = 'Sabotaged Failures')) + geom_bar(stat = "identity", aes(x = partLs, y = partUFailAC, fill = 'Unexplained Failures')) + scale_fill_manual(values = colorSetParts) + labs(x = "Part Minipreps", y = "Number of Assembly Failures", fill = "Failure types") + coord_flip() + theme_grey(base_size = 18)


```
Assembly Pie chart
```{r}
#color set of graph (in RGB)
colorSet4 = c(CSabFail,CSuc,CSabSuc,CAcFail)

assOutcomeLab = c("Sucessful Assemblies", "Sabotaged Failures", "Unexplained Failures", "Sucessful Assemblies \nfrom Threshold Saboteurs")
assOutcomeVal = c(length(assUSuc), length(assUFailSab), length(assUFailAC), length(assUSucSab))
assDF = data.frame(assOutcomeLab, assOutcomeVal)

write.csv(assDF,"/Users/odysseasmorgan/Chemistry/Thesis/Part_Sorting_Code/Assembly_Performance.csv", row.names = FALSE)

ggplot(assDF, aes(x="", y = assOutcomeVal, fill = assOutcomeLab)) + geom_col() + scale_fill_manual(values = colorSet4) + geom_text(aes(label = assOutcomeVal), position = position_stack(vjust = 0.5)) + labs(x = "",y = "Assemblies", fill = "Assembly Outcomes") + coord_polar(theta = "y") + theme_grey(base_size = 18) 


```







```{r}


###Unique assembly suc count

sucURateRaw = length(assUSuc)/(length(assUSuc)+length(assFailRaw) + length(assUSucSab))

sucURateAC = (length(assUSuc))/(length(assUSuc)+length(assUFailAC))

###older measures below, counts all replicates
#raw fail rate

sucRateRaw =  length(assSuc)/(length(assSuc)+length(assFailRaw))

#-2 is to account for successful threshold saboteur m1469
sucRateAC = (length(assSuc)-2)/(length(assSuc)+length(assFailAC)-2)
```

Assembly Success rate breakdown
```{r}
#only counts unique assemblies
sucURateLab = c("All Assemblies", "Non-Sabotaged Assemblies")
sucURateVal = c(sucURateRaw, sucURateAC)

sucRateDF = data.frame(sucURateLab, sucURateVal)


ggplot(data=sucRateDF, aes(x = sucURateLab, y = sucURateVal*100, fill = c('r','b'))) + geom_bar(stat = "identity") + labs(x = "", y = "Success Rate %") + ylim(0,100) + theme_grey(base_size = 18)

```

```





